Modelling BCG vaccination in the UK

### 2019-08-06 rmds/02-background.Rmd
getTBinR plot text size

```{r global-regional-tb-summary, fig.cap = "TB incidence rates (per 100,000) by region and globally from 2000 until 2017. Globally incidence rates have been declining since the early 2000s but this decline varies with region. Plot produced using getTBinR", fig.scap = "TB incidence rates (per 100,000) by region and globally from 2000 until 2017.", out.extra = ""}
plot_tb_burden_summary(conf = NULL, verbose = FALSE, viridis_end = 1)
```

@@

```{r map-global-tb, fig.cap = "Global map of country level TB incidence rates (per 100,000 population) in 2017. Note the clustering of countries with high incidence rates in southern and central Africa and southern Asia. Incidence rates in the legend refer to the lower bound for each colour. Map produced using getTBinR", fig.scap = "Global map of country level TB incidence rates (per 100,000 population) in 201", fig.height = 4}
map_tb_burden(verbose = FALSE)
```

@@

```{r global-regional-mortality-summary, fig.scap =  "TB mortality rates (per 100,000 cases) by region and globally from 2000 until 2017.", fig.cap = "TB mortality rates (per 100,000 cases) by region and globally from 2000 until 2017. Mortality rates from TB have been falling in all regions since 2000. Plot produced using getTBinR", out.extra = ""}
plot_tb_burden_summary(conf = NULL, verbose = FALSE, metric = "e_mort_100k", 
                       denom = "e_inc_num", facet = "Area", legend = "none", 
                       scales = "free_y") 
```

@@

```{r map-global-tb-with-hiv, fig.scap = "Global map of estimated HIV in incidence TB (percent) in 2017.", fig.cap = "Global map of estimated HIV in incidence TB (percent) in 2017. Note the high percentage of TB cases with HIV in sub-saharan Africa. The percentages of HIV in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR", fig.height = 4}
map_tb_burden(metric = "e_tbhiv_prct", verbose = FALSE)
```

@@

```{r map-global-tb-with-rr, fig.scap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017.", fig.cap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017. Note that a far higher percentage of TB cases have rifampicin resistance in the former Soviet Union that in the rest of the world. The percentages of rifampicin resistances in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR (see \\@ref(getTBinR) for details)", fig.height = 4}
map_tb_burden(metric = "e_rr_pct_new", verbose = FALSE)
```

@@

```{r plot-incidence, echo = FALSE, warning = FALSE, message = FALSE, dpi = 300, fig.height = 12, fig.width = 12, fig.scap = "TB notifications in England and Wales from 1913 to 2017, stratified initially by respiratory/non-respiratory status and from 1982 by pulmonary/non-pulmonary TB.", fig.cap = "TB notifications in England and Wales from 1913 to 2017, stratified initially by respiratory/non-respiratory status and from 1982 by pulmonary/non-pulmonary TB. Interventions are highlighted with vertical lines, with linetype denoting the type of intervention, more information on each intervention is available in the corresponding table. Figure produced using `tbinenglanddataclean`", out.extra = ""}
plot_historic_tb_ew() + theme(legend.position = "top")
```

@@

As TB incidence rates alone cannot be used to assess current TB transmission due to reactivation of those latently infected, the incidence rate in UK born children (0-14 years old) is used as a proxy for transmission. Incidence rates in UK born children have fallen 47% from 3.4 per 100,000 in 2008 to 1.8 per 100,000 in 2016.[@PHE2017] This indicates that TB transmission has fallen in the last decade. However, BCG vaccination was introduced for those neonates at high risk of TB in 2005, which may partly be responsible for the observed reduction in incidence rates.

@@

```{r plot-prop-pul, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300, fig.height = 12, fig.width = 12, fig.scap = "From 1913 until 1981 the figure shows the proportion respiratory vs. non-respiratory cases and from 1982 it shows the proportion of pulmonary vs. non-pulmonary TB.", fig.cap = "From 1913 until 1981 the figure shows the proportion respiratory vs. non-respiratory cases and from 1982 it shows the proportion of pulmonary vs. non-pulmonary TB. Figure produced using `tbinenglanddataclean`"}
plot_historic_prop_pul_tb() + theme(legend.position = "top")
```

>>>>

```{r global-regional-tb-summary, fig.cap = "TB incidence rates (per 100,000) by region and globally from 2000 until 2017. Globally incidence rates have been declining since the early 2000s but this decline varies with region. Plot produced using getTBinR", fig.scap = "TB incidence rates (per 100,000) by region and globally from 2000 until 2017.", out.extra = ""}
plot_tb_burden_summary(conf = NULL, verbose = FALSE, viridis_end = 1) + theme(text = element_text(size = 12))
```

@@

```{r map-global-tb, fig.cap = "Global map of country level TB incidence rates (per 100,000 population) in 2017. Note the clustering of countries with high incidence rates in southern and central Africa and southern Asia. Incidence rates in the legend refer to the lower bound for each colour. Map produced using getTBinR", fig.scap = "Global map of country level TB incidence rates (per 100,000 population) in 201", fig.height = 4}
map_tb_burden(verbose = FALSE) + 
  theme(text = element_text(size = 12))
```

@@

```{r global-regional-mortality-summary, fig.scap =  "TB mortality rates (per 100,000 cases) by region and globally from 2000 until 2017.", fig.cap = "TB mortality rates (per 100,000 cases) by region and globally from 2000 until 2017. Mortality rates from TB have been falling in all regions since 2000. Plot produced using getTBinR", out.extra = ""}
plot_tb_burden_summary(conf = NULL, verbose = FALSE, metric = "e_mort_100k", 
                       denom = "e_inc_num", facet = "Area", legend = "none", 
                       scales = "free_y") +
  theme(text = element_text(size = 12))
```

@@

```{r map-global-tb-with-hiv, fig.scap = "Global map of estimated HIV in incidence TB (percent) in 2017.", fig.cap = "Global map of estimated HIV in incidence TB (percent) in 2017. Note the high percentage of TB cases with HIV in sub-saharan Africa. The percentages of HIV in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR", fig.height = 4}
map_tb_burden(metric = "e_tbhiv_prct", verbose = FALSE) +
  theme(text = element_text(size = 12))
```

@@

```{r map-global-tb-with-rr, fig.scap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017.", fig.cap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017. Note that a far higher percentage of TB cases have rifampicin resistance in the former Soviet Union that in the rest of the world. The percentages of rifampicin resistances in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR (see \\@ref(getTBinR) for details)", fig.height = 4}
map_tb_burden(metric = "e_rr_pct_new", verbose = FALSE) + 
  theme(text = element_text(size = 12))
```

@@

```{r plot-incidence, echo = FALSE, warning = FALSE, message = FALSE, dpi = 300, fig.height = 12, fig.width = 12, fig.scap = "TB notifications in England and Wales from 1913 to 2017, stratified initially by respiratory/non-respiratory status and from 1982 by pulmonary/non-pulmonary TB.", fig.cap = "TB notifications in England and Wales from 1913 to 2017, stratified initially by respiratory/non-respiratory status and from 1982 by pulmonary/non-pulmonary TB. Interventions are highlighted with vertical lines, with linetype denoting the type of intervention, more information on each intervention is available in the corresponding table. Figure produced using `tbinenglanddataclean`", out.extra = ""}
plot_historic_tb_ew() + theme(legend.position = "top")+ 
  theme(text = element_text(size = 12))
```

@@

As TB incidence rates alone cannot be used to assess current TB transmission, due to reactivation of those latently infected, the incidence rate in UK born children (0-14 years old) is often used as a proxy for transmission. Incidence rates in UK born children have fallen 47% from 3.4 per 100,000 in 2008 to 1.8 per 100,000 in 2016.[@PHE2017] This indicates that TB transmission has fallen in the last decade. However, BCG vaccination was introduced for those neonates at high risk of TB in 2005, which may partly be responsible for the observed reduction in incidence rates.

@@

```{r plot-prop-pul, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300, fig.height = 12, fig.width = 12, fig.scap = "From 1913 until 1981 the figure shows the proportion respiratory vs. non-respiratory cases and from 1982 it shows the proportion of pulmonary vs. non-pulmonary TB.", fig.cap = "From 1913 until 1981 the figure shows the proportion respiratory vs. non-respiratory cases and from 1982 it shows the proportion of pulmonary vs. non-pulmonary TB. Figure produced using `tbinenglanddataclean`"}
plot_historic_prop_pul_tb() + theme(legend.position = "top") +
  theme(text = element_text(size = 12))
```
